Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-25 presentacion_hiram/presentacion-tesis.tex
revision
remove theme
nuevo

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{\tiny
			L.F. Hiram Ernesto Dami\'an\\
			\vspace{5px}
				Director:\\
					\vspace{5px}
			Jos\'e Feliciano Ben\'itez Rubio\\
				\vspace{5px}
				Maestr\'ia en Ciencias (F\'isica)\\
					\vspace{5px}
			 Departamento de Investigacion en F\'isica }
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	\date{\small November 25$^{th}$ 2019}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18255\\
		\hline
		$tH$	(only)&
		0.015&
		560.39\\
		\hline
	\end{tabular}
\end{table}

@@

\begin{frame}
\frametitle{$\mu\mu$ same sign decay rate}
\tiny{Table of decay chains for tH.  Expected number of $tH$ final states events for 35.9 fb$^{-1}$.l represents $\mu^{\pm},e^- , \tau^\pm$. }
\begin{table}
\renewcommand{\arraystretch}{0.55}
\begin{tabular}{|p{8cm}|p{1.3cm}|c|}
\hline
Decay chain &BR&Events\\
\hline 
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  1.173  \\
\hline
\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.899 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.203 \\
\hline
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.105  \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
\tiny{1.681 $\times$10$^{-4}$} & 0.094 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.017\\
\hline
\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.011\\
\hline 
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.008  \\
\hline
%\tiny{$tH \rightarrow$W$^+$bZ$\gamma$ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- \gamma$} & \tiny{6.888$\times$10$^{-6}$}&0.003\\
%\hline 
%\tiny{$tH \rightarrow$W$^+$bZZ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- l^+l^-$} &\tiny{3.962$\times$10$^{-6}$ }&0.002\\
%\hline 
%%\tiny{$tH \rightarrow$ $\tau \nu_\tau $bZ$\gamma$ $\rightarrow$ $\mu^- \bar{\nu_\mu} \nu_\tau \nu_\tau$ b $\mu^+ \mu^- \gamma$} & 6.347$\times$10$^{-7}$ & 0.0003\\
%%\hline 
\end{tabular}
\end{table}
\end{frame}

@@

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \small{$W\rightarrow$ $q\bar{q}$}
\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item a light-flavor quark 
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

@@

\begin{frame}
\subsection{Systematic uncertainties}
\frametitle{Systematic uncertainties}
\begin{itemize}
	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
\end{itemize}

\begin{frame}
\section{Statistical analysis}
\frametitle{Fitting}
	\begin{center}
	\begin{figure}
		\includegraphics[width=10.5cm]{figures/fit-box.png}
		\caption*{}
	\end{figure}
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Results}
\framesubtitle{Upper limit}
\tiny{
\begin{table}[ht!]
	\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit & $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit \\
		\hline
		35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
		\hline
		150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
		\hline
		300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
		\hline
		3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 1.1\\
		\hline
	\end{tabular}
	\label{upper}
\end{table}
}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\item The results of the analysis for the SM case indicates that it is impossible to detect a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
\item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical.
\item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
\end{itemize}
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
%\usetheme{Frankfurt}
\usepackage{tikz} 
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{\tiny
			L.F. Hiram Ernesto Dami\'an\\
			\vspace{5px}
				Director:\\
					\vspace{5px}
			Jos\'e Feliciano Ben\'itez Rubio\\
				\vspace{5px}
				Maestr\'ia en Ciencias (F\'isica)\\
					\vspace{5px}
			 Departamento de Investigacion en F\'isica }
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	\date{\small November 25$^{th}$ 2019}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
%\item Experimentally
%\begin{align}
%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
%\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18183\\
		\hline
		$tH$ &
		0.074&
		2665\\
		\hline
	\end{tabular}
\end{table}

@@

\begin{frame}
\frametitle{$\mu\mu$ same sign decay rate}
\tiny{Table of decay chains for tH.  Expected number of $tH$ final states events for 35.9 fb$^{-1}$.l represents $\mu^{\pm},e^- , \tau^\pm$. }
\begin{table}
\renewcommand{\arraystretch}{0.55}
\begin{tabular}{|p{8cm}|p{1.3cm}|c|}
\hline
Decay chain &BR&Events\\
\hline 
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  5.58  \\
\hline
\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.89 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.96 \\
\hline
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.50  \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
\tiny{1.681 $\times$10$^{-4}$} & 0.44 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.08\\
\hline
\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.05\\
\hline 
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.04  \\
\hline
%\tiny{$tH \rightarrow$W$^+$bZ$\gamma$ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- \gamma$} & \tiny{6.888$\times$10$^{-6}$}&0.003\\
%\hline 
%\tiny{$tH \rightarrow$W$^+$bZZ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- l^+l^-$} &\tiny{3.962$\times$10$^{-6}$ }&0.002\\
%\hline 
%%\tiny{$tH \rightarrow$ $\tau \nu_\tau $bZ$\gamma$ $\rightarrow$ $\mu^- \bar{\nu_\mu} \nu_\tau \nu_\tau$ b $\mu^+ \mu^- \gamma$} & 6.347$\times$10$^{-7}$ & 0.0003\\
%%\hline 
\end{tabular}
\end{table}
\end{frame}

@@

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \small{$W\rightarrow$ $q\bar{q}$}
%\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item A light-flavor quark (Forward jet)
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

@@

\begin{frame}
\subsection{Systematic uncertainties}
\frametitle{Systematic uncertainties on the yields}
\begin{itemize}
\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
\item In the Rare background, a $50\%$ of uncertainty is assigned.
\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters (e.g. the strong coupling constant $\alpha_s$ and Parton Distribution Functions (PDF) ) used in that simulation.
\end{itemize}
\end{frame}

%\begin{frame}
%\section{Statistical analysis}
%\frametitle{Fitting}
%	\begin{center}
%	\begin{figure}
%		\includegraphics[width=10.5cm]{figures/fit-box.png}
		\caption*{}
%	\end{figure}
%\end{center}
%\end{frame}

@@

\begin{frame}
\frametitle{Results}
\framesubtitle{Upper limit}
		\begin{table}[ht]
		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
			\hhline{~----}	&$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
			\hline
			35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
			\hline
			150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
			\hline
			300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
			\hline
			3000&1.0 $\pm$ 1.7 & 4.3 & 1.0 $\pm$ 0.1 & 0.9-1.1\\
			\hline
		\end{tabular}
		\label{upper}
	\end{table}

}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
\item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical.
\item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
\end{itemize}
\end{frame}
